---
title: "Open Science Office Kick-Off"
subtitle: "Analysis and Executive Summary"
author: Sabou Rani Stocker
date: 2026-02-24
format:
  html:
    theme: [sandstone, ../styles/hsg_pages.scss]
execute:
  echo: false      # hide code
  warning: false   # hide warnings
  error: false     # hide errors
  message: false   # hide messages
project: "aPKM"
bibliography: ../bibliography.bib
navbar: false
---

# Executive Summary

# Main Event

The main event was an overall success with 4 participants online and approximately 25 participants in person. Some fun statistics: 

- 

## Timing

Our timing-planning was surprisingly accurate. 
```{r}
library(ggplot2)
library(tidyr)
library(dplyr)

timing_main <- data.frame(
  section = c("Speech","Intro","Office","Library","Alexandria","Speaker1","Speaker2","Speaker3","Discussion","Ending"),
  estimates = c(3,10,5,3,3,3,3,3,15,5),
  actual = c(5,12,4,4,4,4,3,4,20,3)
)

timing_main$section <- factor(timing_main$section, 
                              levels = timing_main$section)

# reshape to long format
timing_long <- timing_main %>%
  pivot_longer(cols = c(estimates, actual),
               names_to = "type",
               values_to = "minutes")

# plot
ggplot(timing_long, aes(x = section, y = minutes, 
                        color = type, group = type)) +
  geom_line() +
  geom_point(size = 3) +
  labs(x = "Section", y = "Minutes",
       color = "Legend") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

timing_long <- timing_main %>%
  pivot_longer(cols = c(estimates, actual),
               names_to = "type",
               values_to = "minutes") %>%
  group_by(type) %>%
  arrange(section, .by_group = TRUE) %>%
  mutate(cum_minutes = cumsum(minutes))

ggplot(timing_long, aes(x = section, y = cum_minutes,
                        color = type, group = type)) +
  geom_line() +
  geom_point(size = 3) +
  labs(x = "Section", y = "Cumulative Minutes", color = "") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Feedback Main Event

none yet. 

# Apéro

## Hypothesis 1
At least one person will ask for the recipe for the cookies.

```{r}
h1_df <- data.frame(
  oc_question = c(0,0,0,0,0),
  time_question = c(0,0,0,0,0)
)
```

The hypothesis was not accepted. While there were a lot of people complimenting the baked goods, noone asked for the recipe. The theory that people ask for a recipe to be polite has been rejected. 

## Hypothesis 2
The cookies will be gone before the muffins.

```{r}
h2_df <- data.frame(
  count_cookies = c(5,10,15,20,25,30,35,40),
  time_cookies = c(10,15,35,65,0,0,0,0)
)

# remove zero-time rows
h2_df_clean <- h2_df %>%
  filter(time_cookies > 0)

ggplot(h2_df_clean, aes(x = time_cookies, y = count_cookies)) +
  geom_line() +
  geom_point(size = 3) +
  labs(x = "Time (minutes)", 
       y = "Cookies eaten (cumulative)") +
  theme_minimal()
```

Surprisingly based on previous data from the IBT, Hypothesis 2 was rejected. While neither cookies nor muffins were completely finished, after 65 minutes, 18 cookies were left (22 cookies were eaten), while only 9 muffins were left (5 raspberry, 2 apricot, 2 blueberry). Accounting for the different amount of cookies vs. muffins, $\frac{17}{40} = 0.425$ cookies remained, and $frac{9}{36} = 0.25$ muffins remained. 

## Hypothesis 3
The blueberry muffins and/or the raspberry muffins will be eaten faster than the apricot muffins.

```{r}
h3_df <- data.frame(
  type_muffins = c("Raspberry","Raspberry","Raspberry","Blueberry","Blueberry","Blueberry","Apricot","Apricot","Apricot"),
  count_muffins = c(6,9,10,6,9,12,6,9,12),
  time_muffins = c(45,0,0,30,0,0,20,50,0)
)

h3_clean <- h3_df %>%
  filter(time_muffins > 0)

ggplot(h3_clean, aes(x = time_muffins, 
                     y = count_muffins, 
                     color = type_muffins,
                     group = type_muffins)) +
  geom_line() +
  geom_point(size = 3) +
  labs(x = "Time (minutes)",
       y = "Muffins eaten (cumulative)",
       color = "Muffin type") +
  theme_minimal()

muffins_df <- data.frame(
  N_Muffins = 1:12,
  Raspberry = c(10,12,15,20,35,40,NA,NA,NA,NA,NA,NA),
  Blueberry = c(5,5,7,10,16,20,22,30,45,NA,NA,NA),
  Apricot = c(3,3,5,7,10,22,25,35,60,NA,NA,NA)
)

muffins_long <- muffins_df %>%
  pivot_longer(cols = c(Raspberry, Blueberry, Apricot),
               names_to = "Type",
               values_to = "Time") %>%
  filter(!is.na(Time))

ggplot(muffins_long,
       aes(x = Time,
           y = N_Muffins,
           color = Type,
           group = Type)) +
  geom_line() +
  geom_point(size = 3) +
  labs(x = "Time (minutes)",
       y = "Number of Muffins Eaten",
       color = "Muffin Type") +
  theme_minimal()

```

This hypothesis was partially accepted. While two blueberry muffins and two apricot mufffins remained in the end, the blueberry muffins were eaten faster than the apricot muffins. Only after ~65 minutes, the 9th apricot muffin was eaten. 

## Hypothesis 4
At least one person will scan the QR code explaining the badges.

```{r}
h4_df <- data.frame(
  oc_qrcode = c(1,0,0,0,0),
  time_qrcode = c(20,0,0,0,0)
)
```

Hypothesis 4 was confirmed. Exactly one person scanned the QR code. 

# After-Effects

## Newsletter Sign-up

## Emails

## Websitenbesuche

Directly after the kick-off, 7 people visited the website, of which 2 people had IP addresses from Germany (presumably David and someone else). 